Recalibrating Gravitational Wave Phenomenological Waveform Model

### 2023-06-28 src/tex/ms.tex
final check

We divided the parameter space into four regions to analyze the effect of the
recalibration procedure on each region separately
(Fig.~\ref{fig:all_quadrants}~and~\ref{fig:ps_q148_quadrant}). The training waveforms used for fitting in
this scenario are listed in Tab.~\ref{tab:quadrants} and the loss functions 
are calculated using a simple average of the mismatches, $\mathcal{L}_{\mathrm{ave}}$. The top-left and
bottom-right regions have limited data for $q>4$, hence the result is only valid up to $q\leq4$ and we take waveforms with $q\leq4$ as validation waveforms in these two regions. From top panel of Fig.~\ref{fig:ps_q148_quadrant}, we observe that
equal-spin waveforms lying on the diagonal improve the most. 
\kl{Both top-right and bottom-left region have good performance comparing with the original model. Especially for the bottom-left region, where the improvement is significantly better than optimizing all regions simultaneously. This suggests the ansatz are well-fitted to this part of the parameter space.
Waveforms above the diagonal also give good improvements when comparing with the original model and it has a similar improvement as optimizing all waveforms at once. Notice optimizing all regions gives a slightly better improvement. This shows that the ansatz can achieve a better fit using training waveforms with similar spins, even for waveforms with non-equal spin parameters.}
%The improvement above the diagonal is also significantly more than when optimizing using
%all waveforms at once. This can be seen clearly in the top panel of Fig.~\ref{fig:all_quadrants}, where we see
%that the optimized histogram shifts to lower mismatches.
\footnote{
	Note that the bottom-left panel of Fig.~\ref{fig:all_quadrants} specifically shows the
	distribution of mismatches for the top-left quadrant of Fig.~\ref{fig:ps_q148_quadrant}.
} 
On the other hand, the improvement below the diagonal is negligible, indicating that our method struggles to
further improve over the original IMRPhenomD waveform. 
Interestingly, we can see in the bottom-right region that the waveform does not show a significant change
to the overall mismatch (see bottom-right panel of Fig.~\ref{fig:all_quadrants}). 
This suggests that the IMRPhenomD waveform ansatz fits waveforms with
$\chi_1>0$ and $\chi_2<0$ less well. 
\kl{Overall, the improvement for both optimization schemes are similar (bottom panel of Fig.~\ref{fig:ps_q148_quadrant}). Although split region optimization uses more training waveforms, some of the waveforms, e.g. opposite spins, hinders the optimization procedure and hence gives a slightly worse result when comparing with all region optimization.}

>>>>

We divided the parameter space into four regions to analyze the effect of the
recalibration procedure on each region separately
(Fig.~\ref{fig:all_quadrants}~and~\ref{fig:ps_q148_quadrant}). The training waveforms used for fitting in
this scenario are listed in Tab.~\ref{tab:quadrants} and the loss functions 
are calculated using a simple average of the mismatches, $\mathcal{L}_{\mathrm{ave}}$. The top-left and
bottom-right regions have limited data for $q>4$, hence the result is only valid up to $q\leq4$ and we take waveforms with $q\leq4$ as validation waveforms in these two regions. 
\kl{From Fig.~\ref{fig:all_quadrants}, we observe that both top-right and bottom-left region have good performance comparing with the original model. Especially for the bottom-left region, where the improvement is significantly better than optimizing all regions simultaneously. This suggests the ansatz are well-fitted to this part of the parameter space.
Waveforms lying in the top-left region also give good improvements when comparing with the original model and it has a similar improvement as optimizing all waveforms at once. Notice optimizing all regions gives a slightly better improvement. This shows that the ansatz can achieve a better fit using training waveforms with similar spins, even for waveforms with non-equal spin parameters.}
On the other hand, the improvement in the bottom-right region is negligible, indicating that our method struggles to
further improve over the original IMRPhenomD waveform. 
Interestingly, we can see in the bottom-right region that the waveform does not show a significant change
to the overall mismatch (see bottom-right panel of Fig.~\ref{fig:all_quadrants}). 
This suggests that the IMRPhenomD waveform ansatz fits waveforms with
$\chi_1>0$ and $\chi_2<0$ less well. 
\kl{Overall, the improvement for both optimization schemes are similar (Fig.~\ref{fig:ps_q148_quadrant}). Although split region optimization uses more training waveforms, some of the waveforms, e.g. opposite spins, hinders the optimization procedure and hence gives a slightly worse result when comparing with all region optimization.}
